An Audio Interface for an Active Perception Navigation Aid for Blind People

### 2019-05-14 article.tex
Cut out a bunch of sections with blind people and Fitts law stuff

The main contributions of this paper are two-fold:

\begin{itemize}
  \item we provide the first experimental results on how well a tone with varying pitch can convey a target's tilt angle when using a mobile device with bone-conducting headsets; 
  \item we show that this sound-based human-machine interface conforms to Fitts's Law and can provide a useful metric of performance for similar mobile user interfaces.
\end{itemize}

>>>>

This work contributes by providing the first experimental results on how well a tone with varying pitch can convey a target's tilt angle when using a mobile device with bone-conducting headsets.

%The main contributions of this paper are two-fold: 
%\begin{itemize}
  %\item we provide the first experimental results on how well a tone with varying pitch can convey a target's tilt angle when using a mobile device with bone-conducting headsets; 
  %\item we show that this sound-based human-machine interface conforms to Fitts's Law and can provide a useful metric of performance for similar mobile user interfaces.
%\end{itemize}
